### 2015-10-06 definition.tex
Removing unused content

In a filesystem, the contents of a path can be broken (\(F(\pi)=\ud\),
if the file or directory does not exist), they can be
a file (\(F(\pi)=\cfile{X}\)) or a directory (\(F(\pi)=\cdir{Y}\)).  
We also write \(X\) or \(Y\) for some unspecified but non-\(\ud\)
contents.
\begin{notrsi} 
In real-life filesystems, files and directories can carry additional information
like modification times, permissions, etc.
Here we consider these included in the contents. 
\end{notrsi}

@@

\begin{notrsi}
\begin{itemize}
\item
\(create(\pi,X)\) modifies \(F(\pi)\) to \(X\) iff
\(F(\pi)\) is broken and its parent is a directory; i.e.
\[create(\pi,X)F=
\begin{cases}
F\{\pi\mapsto X\}, &\mbox{iff~} F(\pi)=\ud
\wedge F(parent(\pi))=\cdir{Y}\\
\ud, &\mbox{otherwise.}
\end{cases}\]
\item
The command \(edit\) can change the type of a path (file or
directory) according to its second argument.
Since the tree property must be preserved, the definition is:
\begin{align*}
edit(\pi,\cdir{X})F&=
\begin{cases}
F\{\pi\mapsto \cdir{X}\}, &\mbox{iff~}
F(\pi)\neq\ud\\
\ud &\mbox{otherwise;}
\end{cases}\\
edit(\pi,\cfile{X})F&=
\begin{cases}
F\{\pi\mapsto\cfile{X}\} &\mbox{iff~}
F(\pi)\neq\ud\wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}
\end{align*}
\item
\(remove(\pi)\) only removes files or directories without files:
\[remove(\pi)F=
\begin{cases}  
F\{\pi\mapsto\ud\} &\mbox{iff~}
F(\pi)\neq\ud \wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}\]
\item
\(break\) breaks the filesystem:
\[\begin{array}{r@{}ll}
breakF&{}=\ud &\mbox{for every $F$.}\end{array}\]
\end{itemize}
\end{notrsi}
%
\begin{forrsi}
{\small{
%\begin{align}
\begin{gather*}\begin{array}{r@{}ll}
create(\pi,X)F&{}=F\{\pi\mapsto X\}, 
&\mbox{iff~}(F(\pi)=\ud)\wedge(F(parent(\pi))=\cdir{Y})\\
&{}=\ud, &\mbox{otherwise.}\\
edit(\pi,\cdir{X})F&{}=F\{\pi\mapsto \cdir{X}\}, 
&\mbox{iff~}F(\pi)\neq\ud\\
&{}=\ud &\mbox{otherwise;}\\
edit(\pi,\cfile{X})F&{}=F\{\pi\mapsto\cfile{X}\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\  
&{}=\ud &\mbox{otherwise.}\\
remove(\pi)F&{}=F\{\pi\mapsto\ud\} 
&\mbox{iff~}(F(\pi)\neq\ud)\wedge(childless_F(\pi))\\
&{}=\ud &\mbox{otherwise.}\\
breakF&{}=\ud &\mbox{for every $F$.}
\end{array}\end{gather*}
%\end{align}
}}
\end{forrsi}
%%%%%%%%%% TAGS!
We write \(\emptyseq\) for the empty sequence of commands.

>>>>

In a filesystem, the contents of a path can be broken (\(F(\pi)=\ud\),
if the file or directory does not exist), they can be
a file (\(F(\pi)=\cfile{X}\)) or a directory (\(F(\pi)=\cdir{Y}\)).  
We also write \(X\) or \(Y\) for some unspecified but non-\(\ud\)
contents.
In real-life filesystems, files and directories can carry additional information
like modification times, permissions, etc.
Here we consider these included in the contents.

@@

\begin{itemize}
\item
\(create(\pi,X)\) modifies \(F(\pi)\) to \(X\) iff
\(F(\pi)\) is broken and its parent is a directory; i.e.
\[create(\pi,X)F=
\begin{cases}
F\{\pi\mapsto X\}, &\mbox{iff~} F(\pi)=\ud
\wedge F(parent(\pi))=\cdir{Y}\\
\ud, &\mbox{otherwise.}
\end{cases}\]
\item
The command \(edit\) can change the type of a path (file or
directory) according to its second argument.
Since the tree property must be preserved, the definition is:
\begin{align*}
edit(\pi,\cdir{X})F&=
\begin{cases}
F\{\pi\mapsto \cdir{X}\}, &\mbox{iff~}
F(\pi)\neq\ud\\
\ud &\mbox{otherwise;}
\end{cases}\\
edit(\pi,\cfile{X})F&=
\begin{cases}
F\{\pi\mapsto\cfile{X}\} &\mbox{iff~}
F(\pi)\neq\ud\wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}
\end{align*}
\item
\(remove(\pi)\) only removes files or directories without files:
\[remove(\pi)F=
\begin{cases}  
F\{\pi\mapsto\ud\} &\mbox{iff~}
F(\pi)\neq\ud \wedge childless_F(\pi)\\
\ud &\mbox{otherwise.}
\end{cases}\]
\item
\(break\) breaks the filesystem:
\[\begin{array}{r@{}ll}
breakF&{}=\ud &\mbox{for every $F$.}\end{array}\]
\end{itemize}

We write \(\emptyseq\) for the empty sequence of commands.
